%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Android and Odoo Developer} % Job title
    {Nibble Softworks} % Organization
    {Bandung, Jawa Barat, Indonesia} % Location
    {June 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Building an ERP system and Point of Sales system for an electronic store company.
        \item Building a custom Odoo 12.0 module for their ERP system. Develop the ERP that covers from management system of the employees, products, accountings, reports, to Point of Sales system.
        \item Building an Android App from scratch to ready-to-use. Develop the Android app using Android native technology that mainly used for supporting the Point of Sales system.
        \item Integrate the ERP system (Odoo) with the Android app to support their Point of Sales system. Creating RESTful API's and access them in the Android app to support communication between the Android app and the ERP system.
        \item Building a custom web page for supporting the Point of Sales system to ease the cashier interaction with the system. Develop functionality of scanning barcode and send the data directly to the web page, printing receipt with special POS printer from a web page using QZ Tray technology, and design plus develop the UI for the web page using HTML & CSS.
        \item Deploy the system to the store and does user training to their employees.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Lecturer} % Job title
    {Parahyangan Catholic University} % Organization
    {Bandung, Jawa Barat, Indonesia} % Location
    {Aug. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Assisting the lecturer in Object-Oriented Programming course and Database Management System course.
        \item Assist students to solve their problem correctly and nicely that following the best practices in programming.
        \item Discussing something that students don't understand at some topic or problem and explaining again the programming concept which they don't grasp correctly.
        \item Assess the student's assignment according to the correct answer and the best practices in programming.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Engineer} % Job title
    {Nibble Softworks} % Organization
    {Bandung, Jawa Barat, Indonesia} % Location
    {Sep. 2017 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Freelancing as a software engineer. Got the projects from the Nibble Softworks company. Building an information system using Odoo ERP. Have done 4 (mostly parts of) information system projects and 1 web development project.
        \item Building a custom Odoo 10.0 module as a management system for Nibble Softworks.
        \item Migrate an e-commerce website for sportswear store from desktop version website to become a mobile-friendly website. Using HTML & CSS technology and Bootstrap 4.0 UI framework for supporting the mobile-friendly part of the website
        \item Develop part of ERP using Odoo for harbour company. Maintaining and updates a lot of JavaScript part of the website to representing maps of the harbour using Scalable Vector Graphics (SVG) which interactively can be filled with data.
        \item Develop part of the management system and accounting information system using Odoo for a textile company. Solve a lot of accounting problem which supported by Odoo built-in module.
        \item Develop updates of management system using Odoo for Sistem Informasi Basis Data Anggota Ordo Santa Ursula Provinsi Indonesia (Sibas OSU). Create a lot of printing reports feature that turn data from the ERP to PDF and Excel format.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
